### 2015-04-06 cug_paper/04_futurework.tex

The authors work in a group that is not dedicated to pure research; part of the group's mandate is to deploy useful software in the production environment.  As such, the most important piece of future work is to convert this demonstration code into a package that can actually be used by other applications running on Titan.  In the introduction, the authors noted that one of the reasons some applications haven't been converted to use the GPU for calculations is that the applications' developers haven't had time.  With that in mind, it's impractical to expect those same developers to make major changes in order to use this code.

The authors are considering a number of methods of packaging this code to make it easy for other developers to integrate into their own applications.  One possibility is to intercept certain POSIX function calls, such as \texttt{open()} and \texttt{write()}, among others.  While somewhat tricky to implement, this technique has been used with good success by the Mercury Posix project.\cite{mercury_posix_demo}  A second possibility is to modify one or more I/O libraries that are popular with applications, such as the NetCDF library, to make use of this code.  This has the advantage of requiring zero code changes by the application developers.  Properly maintaining the modified I/O libraries could be a real problem, though. A final possibility is to integrate this code into the Functional Partitioning project that the authors and their colleagues are working on.\cite{Li:2010:FPO:1884643.1884686}  Obviously, the authors could choose more than one of these alternatives.

@@

Another feature the authors would like to add is the ability to use regular system RAM in addition to the GPU RAM.  It's well known that some applications don't use all the RAM on the compute node.  It's debatable whether letting the daemon use the memory is better than simply letting the operating system use it as page cache.  However, both the Linux kernel page cache and the client-side cache have fairly low limits on the amount of dirty pages they will allow.  Some very basic initial testing implies that allowing the daemon to allocate memory may be more useful than letting the OS use the same memory for page cache, but further testing is required to be certain.

>>>>

The authors work in a group that is not dedicated to pure research; part of the group's mandate is to deploy useful software in the production environment.  As such, the most important piece of future work is to convert this demonstration code into a package that can actually be used by other applications running on Titan.  In the introduction, the authors noted that one of the reasons some applications have not been converted to use the GPU for calculations is that the scientific applications' developers have not had time and/or funding.  With that in mind, it is impractical to expect those same developers to make major changes in order to use this code.

The authors are considering a number of methods of packaging this code to make it easy for application developers to integrate into their own applications.  One possibility is to intercept certain POSIX function calls, such as \texttt{open()} and \texttt{write()}, among others.  While somewhat tricky to implement, this technique has been used with good success by the Mercury Posix project.\cite{mercury_posix_demo}  A second possibility is to modify one or more I/O libraries that are popular with applications, such as the NetCDF library, to make use of this code.  This has the advantage of requiring zero code changes by the application developers.  Properly maintaining the modified I/O libraries could be a real problem, though. A final possibility is to integrate this code into the Functional Partitioning project that the authors and their colleagues are working on.\cite{Li:2010:FPO:1884643.1884686}  Obviously, the authors could choose more than one of these alternatives.

@@

Another feature the authors would like to add is the ability to use regular system RAM in addition to the GPU RAM.  It is well known that some applications do not use all the RAM on the compute node.  It is debatable whether letting the daemon use the memory is better than simply letting the operating system use it as page cache.  However, both the Linux kernel page cache and the client-side cache have fairly low limits on the amount of dirty pages they will allow.  Some very basic initial testing implies that allowing the daemon to allocate memory may be more useful than letting the OS use the same memory for page cache, but further testing is required to be certain.
